---
title: "How to use glatosQAQC to summarize Vemco VRL files"
author: "Todd Hayden"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{glatosQAQC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Background

Vemco vrl files are a proprietary file format that contains data from
acoustic tag detections.  In addition to tag detections, the VRL file
also contains data about receiver operating settings, receiver battery
condition, errors associated with the receiver, time correction
information, review available receiver memory, and many other
settings.  Verifing the integrety of vrl files is an important step to
make sure files are not corrupt and prevent loss of data.

The glatosQAQC package provides a single R function that allows the
user to interactively select vrl files for inclusion in the report.
After vrl files are chosen, the function opens each vrl, extracts
critical metrics from the file and creates a table that contains
information for each receiver.  The generated report is output as an
HTML file and csv file that may be opened in any web browser or
spreadsheet software.

The function performs several basic checks of the data to identify
potential errors or problems.  If any of these checks fail, the column
associated with the error is highlighted in red.  Report also includes
information about time synchronization of computer clock and receiver
clock.  Synchonization of computer clock is checked by comparing
network time local computer time.  Table below describes information
in report.

## Output dictionary
*(table- data dictionary needed here)*

##  Data checks performed
*(table of checks performed are needed here!!)* 

The report is created by running the \code{make_report} function.
This function allows the user to identify the user directory and file
name of output files.  Basic use of function is outlined below:


## Basic use:

```{r, eval = FALSE}

library(glatosQAQC)

make_report(output_dir = "~/Desktop", output_file = "my_report.html")
 
```








