---
title: "GlatosQAQC: A graphical tool for summarizing and verifying InnovaSea acoustic receiver log files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GlatosQAQC: A graphical tool for summarizing and verifying InnovaSea acoustic receiver log files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Background

Innovasea vrl files are the primary data file associated with acoustic
receivers.  The successor to Innovasea *.vrl files are *.vdat files.
Both are propriatary files that contain a host of operating and tag
detection information and includes tag detections, receiver operating
settings and schedule, receiver battery condition, errors associated
with the receiver, time correction information, receiver memory, and
many other settings.  Verifing the integrety of vrl and vdat files is
an important step to make sure files are not corrupt and prevent data
loss.

The glatosQAQC package provides a single R function that allows an
user to interactively select vrl or vdat files for inclusion and then
generates a report that summarizes key operating and detection
information extracted for each vrl submitted.  GlatosQAQC opens each
vrl or vdat file, extracts critical metrics from the file, and creates
a table.  The generated report is output as an HTML file that may be
opened in any web browser or, optionally, output may be saved as a csv
file.

The function performs several basic checks of the data to identify
potential errors or problems.  If any of these checks fail, the column
associated with the error is highlighted in red.  The report also includes
information about time synchronization of computer clock and receiver
clock.  Synchronization of computer clock is checked by comparing
network time and local computer time, however this feature requires
access to internet and will fail if internet access is not available.

# Basic use:

```{r, eval = FALSE}

# load glatosQAQC package
library(glatosQAQC)

# start app
QAQCapp()
```

Running \code{QAQCapp} will open a local browser window with an action
box at the top left side.  Within the box under the "Action" heading
is a pair of selection buttons that allow the user to specify whether
receiver log files submitted were obtained from recently recovered
receivers or obtained from receivers that have recently undergone the
initialization process in preparation for deployment.  Data management
protocols used by researchers at Hammond Bay Biological Station
require all receivers to be downloaded after initialization but prior
to deployment to capture use-defined receiver settings.  If a user
wishes to distinguish between download of receivers after
"initialization" of receivers and prior to deployment from download of
receivers after deployement, then selection of "Download" and
"Initialize" options will add a column to the output to identify the
purpose of the download.

Files from downloaded receivers (*.vrl or *.vdat) can be selected for inclusion
in the summary by pressing the "Browse" button under "Choose vrl or vdat file"
heading.  Once the file selection box opens, the user navigates to the
desired *.vrl or *.vdat files and selects one or many receivers by pressing
control or shift while clicking on the files.  After desired files are
selected, press "open" to create QAQC summary output as a table next
to the file selection box.  \code{glatosQAQC} is designed to append
results from multiple independent selection events to a single table
that contains results from all receivers.  This feature allows the app
to be opened on a computer at the beginning of the day and continue to
be used incrementically as receivers are recovered and downloaded.
All summary output are displayed in two tables that can be selected by
clicking on either "rec data" or "computer time sync" tabs.

# Output

See table below for definition of receiver information summarized by
glatosQAQC:


| Column            | Description						     |	
|:------------------|:---------------------------------------------------------------|
|File Name	    |	Standard file ID					     |	
|rec num	    |	Receiver serial number					     |	
|rec mod	    |	Receiver model						     |
|rec firmware	    | 	Receiver firmware ID					     |	
|rec map	    |	Receiver map	  					     |
|mem avail	    | 	Memory available for logging detections at time of download  |
|rec init	    | 	Receiver clock time at initialization			     |
|rec download	    | 	Receiver clock time at download				     |
|comp download	    | 	Computer clock time at download				     |
|first det	    | 	Time of first detection after initialization		     |
|last det	    | 	Time of last detection before receiver download		     |
|num det	    |	Number of detections   	      	       			     |
|int tag init	    | 	Time of integrated tag initialization (VR2AR, VR2Tx only)    |
|int tag ID	    |	Integrated tag ID (VR2AR, VR2Tx only) 	      	    	     |
|int tag power	    |	Integrated tag broadcast power (VR2AR, VR2Tx only)	     |
|int tag min delay  |	Integrated tag minimum delay (VR2AR, VR2Tx only)	     |		
|int tag max delay  |	Integrated tag maximum delay (VR2AR, VR2Tx only)	     |
|action	    	    |	Download or Initialize identifier    	   		     |
|NIST time (lcl)    |	Server time (local timezone) obtained from internet	     |
|computer time (lcl)| 	Time as reported by computer 	      	   		     |
|time difference (s)| 	Time difference between server time and computer time	     |
|batt_action	    |   Battery replaced or not identifier                           |	

# Data error checks

GlatosQAQC performs several checks for common issues and if found, highlights text in RED to notify user of potential issues.

| Highlighted text      |Criteria      	      	     	    	   	      	      	     |  
|:----------------------|:-------------------------------------------------------------------|
|last det, rec download |Last detection not on same day as receiver download, no detections|
|first det, rec init|First detection not on same day as receiver initialization| 
|mem avail|Less than 10% of receier memory available|
|time difference (s)|Computer clock is +- 2 seconds from internet time server|



# Download

Output from \code{glatosQAQC} can be downloaded by clicking on the
Download button. This action opens a save dialog box that allows file
to be saved at a user-specified location and name.











